Generality in food webs scales with species richness, not latitude

### 2015-03-24 manuscript/latitudepaper.tex
Making results more readable

Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
Specifically,~\ref{Power} implies a normally-distributed, additive error and~\ref{LogLog} a lognormal,
multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
over another, we follow the recommendations in \citet{Xiao2011} and compared the two
model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
data was then used to test for potential effects of latitude.

@@

For each property in $Z$, $G$, and $V$, we used the form of the equation that was best supported
when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
We then simplified the model. As with the models describing the relationships between latitude and food-web
properties, we calculated the AIC of the maximal and all reduced models, created by systematically removing
all possible combinations of terms. Note that if an interaction term was included in a reduced model, all
associated main effects were also retained. $S$ was included in all reduced models. Reduced models were
identified using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. The best-fitting model
was then determined to be the model with the fewest terms where $\Delta$AIC<2. Where there were several
models with the fewest terms where $\Delta$AIC<2, the model with the lowest AIC in this set was chosen as
the best-fitting model. The best-fitting model was then fit using R~\citep{R} function lm from package stats~\citep{stats}.

@@

@@

For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{LogLog} had a
lower AIC than the corresponding equation~\ref{Power}. This indicates that the
data support an assumption of multiplicative log-normal error better than an
assumption of additive normal error. That is, models where $\epsilon$ is
modelled as an exponent to a multiplicative term (that is, an additive term on
the logarithmic scale) provide a better description of the data than models
where $\epsilon$ is modelled as an additive term on the arithmetic scale
[[That's what this means... not sure if explaining it actually adds anything
though]] .  We therefore used logarithmic-form models when assessing the
effect of latitude on scaling relationships  with $S$.

Contrary to the expected latitudinal gradient, the best-fit version of
equation~\ref{Latfull} for $S$ included a signficant effect of latitude on $S$
in stream webs only ($\alpha_{Latitude:Stream}$=-1.69, $p$=0.007).  This
relationship was robust to the removal of three outliers (post-removal
$\alpha_{Latitude:Stream}$=-1.17, $p$=0.038). The best-fit versions of
equation~\ref{Latfull} for $Z$ and $V$ also included relatioships with
latitude in stream webs ($\alpha_{Latitude:Stream}$=-0.179, $p$=0.007 and
$\alpha_{Latitude:Stream}$=-0.179, $p$=0.007, respectively). However, after
the removal of three outlying stream webs with very high $Z$ and $V$ (two of
which also had unusually high $S$) these relationships were no longer
significant ($\alpha_{Latitude:Stream}$=-0-0.046, $p$=0.373 and
$\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). Marine food webs
had lower $S$, $Z$, $G$, and $V$ than all other web types (post-removal
$\alpha_{Marine}$=-29.5, $p$\textless0.001, $\alpha_{Marine}$=-1.46,
$p$=0.035, $\alpha_{Marine}$=-1.74, $p$=0.0612, and $\alpha_{Marine}$=-1.46,
$p$=0.035, respectively) while stream food webs had higher $G$ than webs from
other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
$p$\textless0.001).

As with $S$, $B$ increased slightly with latitude ($\alpha_{Latitude}$=0.001, $p$=0.139). Unlike with $S$, the scaling 
relationship was stronger in stream food webs ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001). 
Scaling of $I$ with latitude did not vary with latitude or across
ecosystem types. 
As with $S$ and $B$, scaling of $T$ increased slightly with 
latitude ($\alpha_{Latitude}$=0.001, $p$=0.136). As with $S$,
this trend was reversed in stream food webs ($\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and was also reversed in 
lake food webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001).
All of the above trends were robust to the removal of outliers.

@@

The effect of latitude on scaling relationships varied across ecosystem types.
Specialization in lake food webs decreased towards the poles [[LS, Gen, Vul
increased]] (Fig.~\ref{}), while in stream food webs $G$ increased towards the
poles but $Z$ and $V$ were unaffected.  These trends were robust to the
removal of outliers. [[Scaling of BIT with latitude?]]

[[Makes more sense to go property by property, do BIT with S].]

More specifically, the scaling of $V$ with $S$ was slightly stronger towards
the equator in estuarine, marine, stream, and terrestrial food webs
($\alpha_{Latitude}$=-0.001, $p$=0.267) but stronger towards the poles in
stream food webs ($\alpha_{Latitude:Lake}$=0.005, $p$=0.008; Fig.~\ref{}).
This scaling relationship was not consistent across different trophic levels.
Scaling of $V$ with the proportion of basal resources was  stronger towards
the poles in estuarine, lake, and stream food webs
($\alpha_{Latitude}$=-0.007, $p$=0.006),  stronger towards the equator in
terrestrial food webs ($\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002), and
nearly neutral in marine food webs ($\alpha_{Latitude:Marine}$=0.009,
$p$=0.047).  Scaling of $V$ with the proportion of intermediate consumers did
not vary across latitude for any ecosystem type.  Scaling was weaker in lake
and stream ecosystems ($\alpha_{Lake}$=-0.170, $p$=0.019 and
$\alpha_{Stream}$=-0.430, $p$\textless0.001, respectively) than in other
ecosystem types. Scaling of $V$ with the proportion of top predators generally
showed a similar pattern to scaling of $V$ with the proportion of basal
resources. Scaling was slightly stronger towards the equator for lake, marine,
and estuarine food webs ($\alpha_{Latitude}$=-0.001, $p$=0.52) but stronger
towards the poles for terrestrial and stream food webs
($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067;
$\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001).

@@

\section*{Tables}

\begin{table}[!h]
\caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude. Note that none
of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. Each `NA' indicates a term that was not included in the corresponding best-fit model.}
\label{Latlms}
\begin{tabular}{l | l l  l l  l l  l l}

\hline
\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
& $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
\hline
Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{table}

\begin{table}[!h]
\caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude in trophic-species versions of food webs. Note that none
of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. `NA' a term that was not included in the corresponding best-fit model.}
\label{Latlms}
\begin{tabular}{l | l l  l l  l l  l l}

\hline
\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
& $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
\hline
Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{table}

\begin{table}[!h]
\caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness. Each `NA' indicates a term that was not included in the corresponding best-fit model. These models refer to the original versions of food webs. }
\label{Bestfits}
\begin{tabular}{l | l l  l l  l l }
Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
                & \multicolumn{2}{c}{Vulnerability}\\
                & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
\hline
Intercept               &-0.453 & \textless0.001 & -0.249 & \textless0.001 & -0.453 & \textless0.001 \\
log(species)            & 0.419 & \textless0.001 &  0.663 & \textless0.001 &  0.419 & \textless0.001 \\
log(species):Lake       & 0.119 & \textless0.001 & -0.185 & 0.016          &  0.119 & \textless0.001 \\
log(species):Marine     & 0.255 & \textless0.001 &  0.090 & 0.002          &  0.255 & \textless0.001 \\
log(species):Terrestrial& 0.207 & 0.002          & -0.122 & \textless0.001 &  0.207 & 0.002 \\
log(species):Latitude   & 0.004 & \textless0.001 & -0.001 & 0.199          &  0.003 & \textless0.001 \\
log(species):Latitude:Marine&-0.004 & 0.007      &  NA    &  NA            & -0.005 & 0.007 \\
log(species):Latitude:Terrestrial&-0.005 & 0.002 &  NA    &  NA            & -0.005 & 0.002 \\
log(species):Latitude:Lake & NA & NA             &  0.006 & 0.002          &  NA    & NA    \\
\hline
$R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
\hline
\end{tabular}
\end{table}

\begin{table}[!h]
\caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness. Each `NA' indicates a term that was not included in the corresponding best-fit model. These models refer to the trophic species versions of food webs. }
\label{Bestfits}
\begin{tabular}{l | l l  l l  l l }
Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
                & \multicolumn{2}{c}{Vulnerability}\\
                & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
\hline
Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
\hline
$R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!h]
\label{scalingfig}
\includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
\caption{Relationships between species richness and mean links per species, mean generality, and mean 
vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
ecosystem types (N=259 food webs). }
\end{figure}

>>>>

Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
Specifically,~\ref{Power} implies a normally-distributed, additive error and~\ref{Loglog} a lognormal,
multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
over another, we follow the recommendations in \citet{Xiao2011} and compared the two
model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
data was then used to test for potential effects of latitude.

@@

For each property in $Z$, $G$, and $V$, we used the form of the equation that was best supported
when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
We then simplified the model. As with the models describing the relationships between latitude and food-web
properties, we calculated the AIC of the maximal and all reduced models, created by systematically removing
all possible combinations of terms. Note that if an interaction term was included in a reduced model, all
associated main effects were also retained. $S$ was included in all reduced models. Reduced models were
identified using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. The best-fitting model
was then determined to be the model with the fewest terms where $\Delta$AIC\textless2. Where there were several
models with the fewest terms where $\Delta$AIC\textless2, the model with the lowest AIC in this set was chosen as
the best-fitting model. The best-fitting model was then fit using R~\citep{R} function lm from package stats~\citep{stats}.

@@

\section*{Scaling by Trophic Levels}

We were also interested in the ways that scaling relationships with $S$ might
be affected by changes to the distribution of species among trophic levels. To
that end, we repeated all of the above analyses replacing species richness by
proportion of basal resources $B$, proportion of intermediate consumers $I$,
and  proportion of top predators $T$ in turn. All model fitting and model
simplification procedures were identical to those described for species-
richness.

@@

  For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{Loglog} had a
  lower AIC than the corresponding equation~\ref{Power}. This indicates that the
  data support an assumption of multiplicative log-normal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an exponent to a multiplicative term (that is, an additive term on
  the logarithmic scale) provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale
  [[That's what this means... not sure if explaining it actually adds anything
  though]] .  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with $S$.

  Contrary to the expected latitudinal gradient, the best-fit version of
  equation~\ref{Latfull} for $S$ included a signficant effect of latitude on $S$
  in stream webs only ($\alpha_{Latitude:Stream}$=-1.69, $p$=0.007).  This
  relationship was robust to the removal of three outliers (post-removal
  $\alpha_{Latitude:Stream}$=-1.17, $p$=0.038). The best-fit versions of
  equation~\ref{Latfull} for $Z$ and $V$ also included relatioships with
  latitude in stream webs ($\alpha_{Latitude:Stream}$=-0.179, $p$=0.007 and
  $\alpha_{Latitude:Stream}$=-0.179, $p$=0.007, respectively). However, after
  the removal of three outlying stream webs with very high $Z$ and $V$ (two of
  which also had unusually high $S$) these relationships were no longer
  significant ($\alpha_{Latitude:Stream}$=-0-0.046, $p$=0.373 and
  $\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). The best-fit
  version of equation~\ref{Latfull} for $G$ did not include any effect of
  latitude in any ecosystem type. Marine food webs
  had lower $S$, $Z$, $G$, and $V$ than all other web types (post-removal
  $\alpha_{Marine}$=-29.5, $p$\textless0.001, $\alpha_{Marine}$=-1.46,
  $p$=0.035, $\alpha_{Marine}$=-1.74, $p$=0.0612, and $\alpha_{Marine}$=-1.46,
  $p$=0.035, respectively) while stream food webs had higher $G$ than webs from
  other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
  $p$\textless0.001) [[Check streams in $V$, $Z$ for post-removal models]].

  The relationships between $B$, $I$, and $T$ with latitude were broadly similar
  to the relationship between $S$ and latitude. $B$ did not vary significantly
  over latitude except in stream food webs where $B$ increased towards the poles
  ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001), while $I$ did not vary
  significantly with latitude in any ecosystem type. Like $S$, $T$ decreased
  towards the poles in stream food webs ($\alpha_{Latitude}$=0.001, $p$=0.136;
  $\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and also decreased towards the
  poles in lake webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001
  All of these trends were robust to the removal of outliers.

@@

The effect of latitude on scaling relationships with $S$ varied across
ecosystem types. The strength of scaling decreased towards the poles for $Z$,
$G$, and $V$ in lake food webs, while in stream food webs $G$ increased
towards the poles but $Z$ and $V$ were unaffected (Figs.~\ref{LS,Gen,Vul}).
In all other ecosystem types, the strength of scaling of $Z$, $G$, and $V$
with $S$ did not vary over latitude. These trends were all robust to the
removal of outliers. When scaling relationships were broken down across
trophic levels, however, the situation was more complex. Scaling relationships
with $B$, $I$, and $T$ generally did not follow the pattern set by scaling
relationships with $S$.

[[Need to find a way to express the total effect of all the alphas for a given ecotype...]]
[[Perhaps with a nice table to refer to?]]

[[redo the other paragraphs something like this]]
For example, while $V$ increased with $S$ across all ecosystem types, $V$
tended to decrease with increasing $B$ and $I$ (Fig.~\ref{LS}). The scaling of
$V$ with $B$ was stronger towards the poles in estuarine, lake, and stream
food webs ($\alpha_{Latitude}$=-0.007, $p$=0.006), stronger towards the
equator in terrestrial webs ($\alpha_{Latitude:Terrestrial}$=0.013,
$p$=0.002), and weakly related to latitude in marine webs
($\alpha_{Latitude:Marine}$=0.009, $p$=0.047). Scaling of $V$ with $T$ was
also stronger towards the equator in terrestrial webs
($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067,
$\alpha_{Terrestrial}$=-0.093, $p$0.526), while scaling of $V$ with $T$ did
not vary significantly over latitude in estuarine, marine or lake webs
($\alpha_{Latitude}$=-0.001, $p$=0.52). Contrary to the scaling of $V$ with
$B$, scaling of $V$ with $T$ in streams was stronger towards the equator
($\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001,
$\alpha_{Stream}$=-0.822,$p$\textless0.001).

@@

% \section*{Tables}

% \begin{table}[!h]
% \caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude. Note that none
% of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. Each `NA' indicates a term that was not included in the corresponding best-fit model.}
% \label{Latlms}
% \begin{tabular}{l | l l  l l  l l  l l}

% \hline
% \multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
% & $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
% \hline
% Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
% Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
% Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
% Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
% \hline
% \end{tabular}
% \end{table}

% \begin{table}[!h]
% \caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude in trophic-species versions of food webs. Note that none
% of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. `NA' a term that was not included in the corresponding best-fit model.}
% \label{Latlms}
% \begin{tabular}{l | l l  l l  l l  l l}

% \hline
% \multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
% & $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
% \hline
% Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
% Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
% Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
% Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
% \hline
% \end{tabular}
% \end{table}

% \begin{table}[!h]
% \caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness. Each `NA' indicates a term that was not included in the corresponding best-fit model. These models refer to the original versions of food webs. }
% \label{Bestfits}
% \begin{tabular}{l | l l  l l  l l }
% Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
%                 & \multicolumn{2}{c}{Vulnerability}\\
%                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
% \hline
% Intercept               &-0.453 & \textless0.001 & -0.249 & \textless0.001 & -0.453 & \textless0.001 \\
% log(species)            & 0.419 & \textless0.001 &  0.663 & \textless0.001 &  0.419 & \textless0.001 \\
% log(species):Lake       & 0.119 & \textless0.001 & -0.185 & 0.016          &  0.119 & \textless0.001 \\
% log(species):Marine     & 0.255 & \textless0.001 &  0.090 & 0.002          &  0.255 & \textless0.001 \\
% log(species):Terrestrial& 0.207 & 0.002          & -0.122 & \textless0.001 &  0.207 & 0.002 \\
% log(species):Latitude   & 0.004 & \textless0.001 & -0.001 & 0.199          &  0.003 & \textless0.001 \\
% log(species):Latitude:Marine&-0.004 & 0.007      &  NA    &  NA            & -0.005 & 0.007 \\
% log(species):Latitude:Terrestrial&-0.005 & 0.002 &  NA    &  NA            & -0.005 & 0.002 \\
% log(species):Latitude:Lake & NA & NA             &  0.006 & 0.002          &  NA    & NA    \\
% \hline
% $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
% \hline
% \end{tabular}
% \end{table}

% \begin{table}[!h]
% \caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness. Each `NA' indicates a term that was not included in the corresponding best-fit model. These models refer to the trophic species versions of food webs. }
% \label{Bestfits}
% \begin{tabular}{l | l l  l l  l l }
% Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
%                 & \multicolumn{2}{c}{Vulnerability}\\
%                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
% \hline
% Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
% log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
% log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
% log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
% log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
% log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
% log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
% log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
% \hline
% $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
% \hline
% \end{tabular}
% \end{table}

@@

% \begin{figure}[!h]
% \label{scalingfig}
% \includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
% \caption{Relationships between species richness and mean links per species, mean generality, and mean 
% vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
% richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
% reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
% strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
% ecosystem types (N=259 food webs). }
% \end{figure}

\begin{figure}[!h]
\label{props_v_lat}
\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_propsvlat.eps}
\caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability (N=163 food webs). }
\end{figure}

\begin{figure}[!h]
\label{TLs_v_lat}
\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_TLvlat.eps}
\caption{Relationships between latitude and proportions of basal resources, intermediate consumers, and top predators (N=163 food webs). }
\end{figure}

\begin{figure}[!h]
\label{LS}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/LS_nonts.eps}
\caption{Relationships between mean links per species and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs). [[More details needed]]}
\end{figure}

\begin{figure}[!h]
\label{Gen}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/Gen_nonts.eps}
\caption{Relationships between mean generality (number of prey) and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs). [[More details needed]]}
\end{figure}

\begin{figure}[!h]
\label{Vul}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/Vul_nonts.eps}
\caption{Relationships between mean vulnerability (number of predators) and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs). [[More details needed]]}
\end{figure}
